Andres Karjus

### 2017-12-30 index.Rmd
jpg fix

<IMG SRC="IMG_2657.JPG" ALIGN="right" BR CLEAR="left" style="margin-left:10px"; /> 
I am a PhD student in linguistics based at the [Centre for Language Evolution at the University of Edinburgh](http://www.lel.ed.ac.uk/cle/), working on evolutionary variant selection in language with [Kenny Smith](www.lel.ed.ac.uk/~kenny), [Simon Kirby](www.lel.ed.ac.uk/~simon) and [Richard A. Blythe](https://www2.ph.ed.ac.uk/~rblythe3/), utilizing massive corpora and natural language processing to hunt traces of selection and competition between elements of language. My research is supported by a Kristjan Jaak scholarship from the Archimedes Foundation of Estonia (incidentally which is where I am from).

>>>>

<IMG SRC="IMG_2657.jpg" ALIGN="right" BR CLEAR="left" style="margin-left:10px"; /> 
I am a PhD student in linguistics based at the [Centre for Language Evolution at the University of Edinburgh](http://www.lel.ed.ac.uk/cle/), working on evolutionary variant selection in language with [Kenny Smith](www.lel.ed.ac.uk/~kenny), [Simon Kirby](www.lel.ed.ac.uk/~simon) and [Richard A. Blythe](https://www2.ph.ed.ac.uk/~rblythe3/), utilizing massive corpora and natural language processing to hunt traces of selection and competition between elements of language. My research is supported by a Kristjan Jaak scholarship from the Archimedes Foundation of Estonia (incidentally which is where I am from).
